\subsection{Definitions of $E_8$ lattice}

There are several equivalent definitions of the $E_8$ lattice. Below, we formalise two of them, and prove they are equivalent.

\begin{definition}{$E_8$-lattice, Definition 1}\label{E8-Set}\lean{E8.E8-Set}\leanok
  We define the \emph{$E_8$-lattice} (as a subset of $\R^8$) to be
$$\Lambda_8=\{(x_i)\in\Z^8\cup(\Z+\textstyle\frac12\displaystyle )^8|\;\sum_{i=1}^8x_i\equiv 0\;(\mathrm{mod\;2})\}.$$
\end{definition}

\begin{definition}\label{E8-Scaled-Set}\lean{E8.E8-Scaled-Set}\uses{E8-Set}\leanok
  We define the \emph{scaled $E_8$-lattice} (by a real number $c$) as $$c\Lambda_8 = \{c \cdot \vec{v} : \vec{v} \in \Lambda_8\}$$.
\end{definition}

\begin{definition}{$E-8$-lattice, Definition 2}\label{E8-Basis-Vecs}\lean{E8.E8-Matrix}\leanok
  We define the \emph{$E_8$ basis vectors} to be the set of vectors
  \[ \B_8 =
  \left\{
    \begin{bmatrix}
      1 \\ -1 \\ 0 \\ 0 \\ 0 \\ 0 \\ 0 \\ 0
    \end{bmatrix},
    \begin{bmatrix}
      0 \\ 1 \\ -1 \\ 0 \\ 0 \\ 0 \\ 0 \\ 0
    \end{bmatrix},
    \begin{bmatrix}
      0 \\ 0 \\ 1 \\ -1 \\ 0 \\ 0 \\ 0 \\ 0
    \end{bmatrix},
    \begin{bmatrix}
      0 \\ 0 \\ 0 \\ 1 \\ -1 \\ 0 \\ 0 \\ 0
    \end{bmatrix},
    \begin{bmatrix}
      0 \\ 0 \\ 0 \\ 0 \\ 1 \\ -1 \\ 0 \\ 0
    \end{bmatrix},
    \begin{bmatrix}
      0 \\ 0 \\ 0 \\ 0 \\ 0 \\ 1 \\ 1 \\ 0
    \end{bmatrix},
    \begin{bmatrix}
      -1/2 \\ -1/2 \\ -1/2 \\ -1/2 \\ -1/2 \\ -1/2 \\ -1/2 \\ -1/2
    \end{bmatrix},
    \begin{bmatrix}
      0 \\ 0 \\ 0 \\ 0 \\ 0 \\ 1 \\ -1 \\ 0
    \end{bmatrix}
  \right\}
  \]
\end{definition}

\begin{definition}\label{E8-Scaled-Matrix}\lean{E8.E8-Scaled-Matrix}\uses{E8-Basis-Vecs}\leanok
  We define the \emph{scaled $E_8$ basis vectors} (by a real number $c$) to be $c\B_8 = \{c \cdot \vec{v} : \vec{v}\in \B_8\}$.
\end{definition}

% Forward direction hasn't been proven yet
\begin{theorem}\label{E8-defs-equivalent}\lean{E8.E8-Set-eq-span}\uses{E8-Scaled-Set, E8-Scaled-Matrix}%\leanok
  The two definitions above coincide, i.e. $c\Lambda_8 = \mathrm{span}_{\Z}(c\B_8)$.
\end{theorem}
\begin{proof}
  We prove each side contains the other side.

  For a vector $\vec{v} \in \Lambda_8 \subseteq \R^8$, we have $\sum_i \vec{v}_i \equiv 0 \pmod{2}$ and $\vec{v}_i$ being either all integers or all half-integers. After some modulo arithmetic, it can be seen that $\B_8^{-1}\vec{v}$ as integer coordinates (i.e. it is congruent to $0$ modulo $1$). Hence, $\vec{v} \in \mathrm{span}_{\Z}(\B_8)$.

  For the opposite direction, we write the vector as $\vec{v} = \sum_i c_i\B_8^i \in \mathrm{span}_{\Z}(\B_8)$ with $c_i$ being integers and $\B_8^i$ being the $i$-th basis vector. Expanding the definition then gives $\vec{v} = \left(c_1 - \frac{1}{2}c_7, -c_1 + c_2 - \frac{1}{2}c_7, \cdots, -\frac{1}{2}c_7\right)$. Again, after some modulo arithmetic, it can be seen that $\sum_i \vec{v}_i$ is indeed $0$ modulo $2$ and are all either integers and half-integers, concluding the proof.

  (Note: this proof doesn't depend on that $\B_8$ is linearly independent.)
\end{proof}

\subsection{Basic Properties of $E_8$ lattice}

In this section, we establish basic properties of the $E_8$ lattice and the $\B_8$ vectors.

\begin{lemma}\label{E8-Scaled-is-basis}\lean{E8.E8-Scaled-is-basis}\uses{E8-Scaled-Matrix}\leanok
  For nonzero real numbers $c$, the set $c\B_8$ is a $\R$-basis of $\R^8$.
\end{lemma}
\begin{proof}
  It suffices to prove that $\B_8 \in \mathrm{GL}_8(\R)$. We prove this by explicitly defining the inverse matrix $\B_8^{-1}$ and proving $\B_8 \B_8^{-1} = I_8$, which implies that $\det(\B_8)$ is nonzero.
\end{proof}

\begin{lemma}\label{E8-Scaled-Lattice}\lean{E8.E8-Scaled-Lattice}\uses{E8-Scaled-Set, E8-defs-equivalent}\leanok
  For real numbers $c$, $c\Lambda_8$ is an additive subgroup of $\R^8$.
\end{lemma}
\begin{proof}\leanok
  Trivially follows from that $\Lambda_8 \subseteq \R^8$ is the $\Z$-span of $\B_8$ and hence an additive group.
\end{proof}

\begin{lemma}\label{E8-Shortest-Vector}\lean{E8.E8-norm-eq-sqrt-even}\uses{E8-defs-equivalent}\leanok
  All vectors in $\Lambda_8$ have norm of the form $\sqrt{2n}$, where $n$ is a nonnegative inteeger.
\end{lemma}
\begin{proof}
  Writing $\vec{v} = \sum_i c_i\B_8^i$, we have $\|v\|^2 = \sum_i \sum_j c_ic_j (\B_8^i \cdot \B_8^j)$. Computing all $64$ pairs of dot products and simplifying, we get a massive term that is a quadratic form in $c_i$ with even integer coefficients, concluding the proof.
\end{proof}

\begin{lemma}\label{instDiscreteE8ScaledLattice}\lean{E8.instDiscreteE8ScaledLattice}\uses{E8-Shortest-Vector}\leanok
  For nonzero real numbers $c$, $c\Lambda_8$ is discrete, i.e. that the subspace topology induced by its inclusion into $\R^8$ is the discrete topology.
\end{lemma}
\begin{proof}
  We prove this for $c = 1$. Since $\Lambda_8$ is a topological group and $+$ is continuous, it suffices to prove that $\{0\}$ is open in $\Lambda_8$. This follows from the fact that there is an open ball $\B(\sqrt{2}) \subseteq \R^8$ around it containing no other lattice points, since the shortest nonzero vector has norm $\sqrt{2}$.
\end{proof}

\begin{lemma}\label{instLatticeE8}\lean{E8.instIsZLatticeE8ScaledLattice}\uses{instDiscreteE8ScaledLattice, E8-Scaled-is-basis}\leanok
  For nonzero real numbres $c$, $c\Lambda_8$ is a lattice, i.e. it is discrete and spans $\R^8$ over $\R$.
\end{lemma}
\begin{proof}\leanok
  The first part is the above lemma. The second part follows from that $\B_8$ is a basis and hence linearly independent over $\R$.
\end{proof}

\todo{Prove $E_8$ is unimodular.}
\todo{Prove $E_8$ is positive-definite.}

\subsection{The $E_8$ sphere packing}

\begin{definition}\label{E8.E8Packing}\lean{E8.E8Packing}\uses{SpherePacking.balls, E8-Scaled-Lattice}\leanok
  The \emph{$E_8$ sphere packing} is the sphere packing with separation $1$, whose set of centres is $\frac{1}{\sqrt{2}}\Lambda_8$.
\end{definition}

\begin{theorem}\label{E8Packing-density}\uses{E8.E8Packing}
  We have $\Delta_{E_8} = \frac{\pi^4}{384}$.
\end{theorem}
\begin{proof}
  \todo{Finish proof. Preferably we want APIs about fundamental region of lattice, and use that to reduce this theorem to computation inside the fundamental region, and use formula for volume of ball.}
\end{proof}

% TODO: Stuff about the fundamental region
