\subsection{On the Density of Periodic Packings}

We begin by stating and proving a few useful lemmas that bound the densities of arbitrary sphere packings. Let $\Pa \subseteq \R^d$ be a sphere packing. Denote by $X$ its set of centers and by $r$ the corresponding separation radius.

Observe that the finite density evaluated at some $R > 0$ measures the density of sphere packings within a bounded, open ball of radius $R$. As one might expect, there is a relationship between the finite density and the number of centers in the ball of radius $R$.
\begin{lemma}\label{SpherePacking.finiteDensity_le_ge}\lean{SpherePacking.finiteDensity_le_ge}\uses{SpherePacking.finiteDensity}\leanok
  For any $R > 0$,
  \[
    \left|X \cap \mathcal{B}_d\left(R - \frac{r}{2}\right)\right| \cdot \frac{\mathrm{Vol}\left(\mathcal{B}_d\left(\frac{r}{2}\right)\right)}{\mathrm{Vol}(\mathcal{B}_d(R))}
    \leq \Delta_{\mathcal{P}}(R)
    \leq \left|X \cap \mathcal{B}_d\left(R + \frac{r}{2}\right)\right| \cdot \frac{\mathrm{Vol}\left(\mathcal{B}_d\left(\frac{r}{2}\right)\right)}{\mathrm{Vol}(\mathcal{B}_d(R))}
  \]
\end{lemma}
\begin{proof}\uses{SpherePacking}\leanok
  The high level idea is to prove that $\mathcal{P} \cap \mathcal{B}_d(R) = \left(\bigcup_{x \in X} \mathcal{B}_d\left(x, \frac{r}{2}\right)\right) \subseteq \bigcup_{x \in X \cap \mathcal{B}_d\left(R + \frac{r}{2}\right)} \mathcal{B}_d\left(x, \frac{r}{2}\right)$, and a similar inequality for the upper bound. The rest follows by rearranging and usign the fact that the balls are pairwise disjoint. The finer details can be found in the Lean proof.
\end{proof}

Suppose further that $X$ is a periodic packing w.r.t. the lattice $\Lambda \subseteq \R^d$. Let $\mathcal{D}$ be a fundamental region of $\Lambda$, say the parallelopiped defined in the proof of \cref{exists-bounded-fd}, and let $L$ be the bound on the norm of vectors in $\mathcal{D}$ (see \cref{exists-bounded-fd}).

\begin{theorem}\label{lattice-points-bounds}\uses{lattice-points-bounds-proof}
  For real numbers $R > L$, we have the following inequality relating the number of lattice points from $\Lambda$ in a ball with the volume of the ball and the fundamental region $\mathcal{D}$:

  \[
    \frac{\mathrm{Vol}(\mathcal{B}_d(R - L))}{\mathrm{Vol}(\mathcal{D})}
    \leq \left|\Lambda \cap \mathcal{B}_d(R)\right|
    \leq \frac{\mathrm{Vol}(\mathcal{B}_d(R + L))}{\mathrm{Vol}(\mathcal{D})}
  \]
\end{theorem}

The proof can be found at \cref{lattice-points-bounds-proof}.

\begin{theorem}\label{periodic-points-bounds}\uses{periodic-points-bounds-proof}
  For real numbers $R > L$, we have the following inequality relating the number of points from $X$ (periodic w.r.t. $\Lambda$) in a ball with the number of points from $\Lambda$:

  \[
    \left|\Lambda \cap \mathcal{B}_d(R - L)\right|\left|X / \Lambda\right|
    \leq \left|X \cap \mathcal{B}_d(R)\right|
    \leq \left|\Lambda \cap \mathcal{B}_d(R + L)\right|\left|X / \Lambda\right|
  \]
\end{theorem}

The proof can be found at \cref{periodic-points-bounds-proof}.

Finally, when we combine the inequalities above, we need one additional computational lemma.

\begin{lemma}\label{volume-ball-ratio}
  For any constant $C > 0$, we have

  \[
    \lim_{R \to \infty} \frac{\mathrm{Vol}(\mathcal{B}_d(R))}{\mathrm{Vol}(\mathcal{B}_d(R + C))} = 1
  \]
\end{lemma}
\begin{proof}
  Write out the formula for volume of a ball and simplify. More specifically, we have $\mathrm{Vol}(\mathcal{B}_d(R)) = R^d \pi^{d / 2} / \Gamma\left(\frac{d}{2} + 1\right)$, so $\mathrm{Vol}(\mathcal{B}_d(R)) / \mathrm{Vol}(\mathcal{B}_d(R + C)) = R^d / (R + C)^d = \left(1 - \frac{1}{R + C}\right)^d = 1$.
\end{proof}

% \begin{lemma}\label{volume-balls-ratio}\uses{}
%   We have
%
%   \[
%     \lim_{R \to \infty} \frac{
%   \]
% \end{lemma}

% \begin{theorem}\label{}
